---
title: "perma"
author: "Sean Merritt"
date: "4/29/2021"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(psychonetrics)
library(tidyverse)
library(EGAnet)
library(lavaan)
library(apaTables)
library(Hmisc)
library(intergraph)
```

```{r}
dat <- read_csv("~/C - Research/PERMA Networks/PERMA_networks/clean_data.csv")
descrip <- dat %>% select(Race, Gender, Age)

jmv::descriptives(descrip)

descrip %>%
  group_by(Gender) %>%
 count()

descrip %>%
  group_by(Race) %>%
 count()

native = 2 + 3 + 3
asian =  33 + 2
islander = 1 + 1
black = 62 + 4 + 3 + 1 + 2 
hispanic = 21 + + 14
white = 406 + 3+ 4 + 3 + 1 + 2 + 14 + 1 + 1
other = 1 + 2 + 1

data.frame(native, asian, islander, black, hispanic, white, other)
```


```{r include=FALSE}
dat <- read_csv("~/C - Research/PERMA Networks/PERMA_networks/clean_data.csv") %>% 
  select(P1,P2,P3,E1,E2,E3,R1,R2,R3,M1,M2,M3,A1,A2,A3,N1, N2,N3, H1, H2, H3, SWL_1:SWL_5, PANAS_1:PANAS_13, big5_1:big5_15) %>%
  na.omit()

descriptive <- dat %>% 
  rowwise() %>% 
  mutate(P = mean(P1:P3, na.rm = T), 
         E = mean(E1:E3, na.rm = T),
         R = mean(R1:R3, na.rm = T),
         M = mean(M1:M3, na.rm = T),
         A = mean(A1:A3, na.rm = T),
         N = mean(N1:N3, na.rm = T),
         H = mean(H1:H3, na.rm = T),
         SWL = mean(SWL_1:SWL_5, na.rm = T),
         Pos = (PANAS_1 + PANAS_3 + PANAS_5 + PANAS_6 + PANAS_8 + PANAS_11 + PANAS_13),
         Neg = (PANAS_2 + PANAS_4 + PANAS_7 + PANAS_9 + PANAS_10 + PANAS_12)
         ) %>% 
  select(P,E,R,M,A,N,H,
         SWL, 
         Pos, Neg
         ) 
```

# Results
## Descriptives

```{r echo=FALSE}
x <- rbind(c(1,2,3), c(4,5,6), c(7,8,9))
#apply_if(x, upper.tri(x), function(x) x + 5)
apply_if <- function(mat, p, f) {
  # Fill NA with FALSE
  p[is.na(p)] <- FALSE
  mat[p] <- f(mat[p])
  mat
}
apaCorr <- function(mat, corrtype = "pearson") {
  matCorr <- mat
  if (class(matCorr) != "rcorr") {
    matCorr <- rcorr(mat, type = corrtype)
  }

  # Add one star for each p < 0.05, 0.01, 0.001
  stars <- apply_if(round(matCorr$r, 2), matCorr$P < 0.05, function(x) paste0(x, "*"))
  stars <- apply_if(stars, matCorr$P < 0.01, function(x) paste0(x, "*"))
  stars <- apply_if(stars, matCorr$P < 0.001, function(x) paste0(x, "*"))
  # Put - on diagonal and blank on upper diagonal
  stars[upper.tri(stars, diag = T)] <- "-"
  stars[upper.tri(stars, diag = F)] <- ""
  n <- length(stars[1,])
  colnames(stars) <- 1:n
  # Remove _ and convert to title case
  row.names(stars) <- tools::toTitleCase(sapply(row.names(stars), gsub, pattern="_", replacement = " "))
  # Add index number to row names
  row.names(stars) <- paste(paste0(1:n,"."), row.names(stars))
  stars
}

irisStars <- apaCorr(as.matrix(descriptive), corrtype = "pearson")

irisStars %>% 
     knitr::kable("latex",booktabs=TRUE) %>% 
     kableExtra::kable_styling()

descriptive %>% 
  jmv::descriptives(sd =T)
```
## Replication of Goodman et al.

We first ran the same factor analysis found in Goodman et al (2016). We also tested two additional models that consisted of independent factors with and without effective measures. We find all models, with the exception of the independent factors model (with emotion) had adequete fit (see table 2).

```{r message=FALSE, warning=FALSE, include=FALSE}

m1 <- '
P =~ P1 + P2+ P3
E =~ E1  + E2 + E3
R =~ R1 + R2 + R3
M =~ M1 + M2 +M3
A =~ A1 + A2 + A3



SWL =~ SWL_1 + SWL_2 + SWL_3 + SWL_4 + SWL_5
Pos =~ PANAS_1 + PANAS_3 + PANAS_5 + PANAS_6 + PANAS_8 + PANAS_11 + PANAS_13
Neg =~ PANAS_2 + PANAS_4 + PANAS_7 + PANAS_9 + PANAS_10 + PANAS_12

wellbeing =~ P + E + R + M + A + SWL + Pos + Neg
'
fit1b <- sem(m1, data=dat)

model1_results <- summary(fit1b, fit.measures = T)$FIT
chisq <- model1_results[[3]]
df <- model1_results[[4]]
pvalue <- model1_results[[5]]
cfi <- model1_results[[9]]
tli <- model1_results[[10]]
aic <- model1_results[[13]]
bic <- model1_results[[14]]
rmsea <- model1_results[[17]]
one_factor_fit <- data.frame(Model = "One Factor",df, chisq,pvalue,tli, cfi, rmsea,aic,bic)


m2 <- '
P =~ P1 + P2+ P3
E =~ E1  + E2 + E3
R =~ R1 + R2 + R3
M =~ M1 + M2 +M3
A =~ A1 + A2 + A3

SWL =~ SWL_1 + SWL_2 + SWL_3 + SWL_4 + SWL_5
Pos =~ PANAS_1 + PANAS_3 + PANAS_5 + PANAS_6 + PANAS_8 + PANAS_11 + PANAS_13
Neg =~ PANAS_2 + PANAS_4 + PANAS_7 + PANAS_9 + PANAS_10 + PANAS_12

SWB =~  SWL + Neg + Pos
PERMA =~ P + E + R + M + A 

SWB ~~ PERMA
'
fit2 <- sem(m2, data=dat)
summary(fit2, fit.measures = T)
model2_results <- summary(fit1b, fit.measures = T)$FIT
chisq <- model1_results[[3]]
df <- model2_results[[4]]
pvalue <- model2_results[[5]]
cfi <- model2_results[[9]]
tli <- model2_results[[10]]
aic <- model2_results[[13]]
bic <- model2_results[[14]]
rmsea <- model2_results[[17]]
two_factor_fit <- data.frame(Model = "SWB~PERMA",df, chisq,pvalue,tli, cfi, rmsea,aic,bic)

m3 <- '
P =~ P1 + P2+ P3
E =~ E1  + E2 + E3
R =~ R1 + R2 + R3
M =~ M1 + M2 +M3
A =~ A1 + A2 + A3

SWL =~ SWL_1 + SWL_2 + SWL_3 + SWL_4 + SWL_5
Pos =~ PANAS_1 + PANAS_3 + PANAS_5 + PANAS_6 + PANAS_8 + PANAS_11 + PANAS_13
Neg =~ PANAS_2 + PANAS_4 + PANAS_7 + PANAS_9 + PANAS_10 + PANAS_12

SWB =~  SWL + Neg + Pos + P 
PERMA =~ E + R + M + A 

SWB ~~ PERMA
'
fit3 <- sem(m3, data=dat)
model3_results <- summary(fit3, fit.measures = T)$FIT
chisq <- model3_results[[3]]
df <- model3_results[[4]]
pvalue <- model3_results[[5]]
cfi <- model3_results[[9]]
tli <- model3_results[[10]]
aic <- model3_results[[13]]
bic <- model3_results[[14]]
rmsea <- model3_results[[17]]
SWB_plusP_fit <- data.frame(Model = "SWB+P~ERMA",df, chisq,pvalue,tli, cfi, rmsea,aic,bic)

m4 <- '
E =~ E1  + E2 + E3
R =~ R1 + R2 + R3
M =~ M1 + M2 +M3
A =~ A1 + A2 + A3


SWL =~ SWL_1 + SWL_2 + SWL_3 + SWL_4 + SWL_5
Neg =~ PANAS_2 + PANAS_4 + PANAS_7 + PANAS_9 + PANAS_10 + PANAS_12
SWB =~ SWL + Neg
ERMA =~ E + R + M + A 

SWB ~~ ERMA
'
fit4 <- sem(m4, data=dat)
model4_results <- summary(fit4, fit.measures = T)$FIT
chisq <- model4_results[[3]]
df <- model4_results[[4]]
pvalue <- model4_results[[5]]
cfi <- model4_results[[9]]
tli <- model4_results[[10]]
aic <- model4_results[[13]]
bic <- model4_results[[14]]
rmsea <- model4_results[[17]]
no_hap_fit <- data.frame(Model = "SWB~ERMA",df, chisq,pvalue,tli, cfi, rmsea,aic,bic)




cfa_results <- one_factor_fit %>% 
  rbind(two_factor_fit) %>% 
  rbind(SWB_plusP_fit) %>% 
  rbind(no_hap_fit)  

names(cfa_results) <- c("Model","df", "$\\chi^2$", "p", "TLI", "CFI", "RMSEA","AIC", "BIC")
```

```{r fit table3, echo=FALSE}
cfa_results %>% 
knitr::kable("latex",booktabs=TRUE) %>% 
     kableExtra::kable_styling()
```

```{r}
semGraph <- function(fit, plot_name, layout = lay, angle = 180){
  prepare_graph(fit, layout = layout, angle = angle) %>% 
  edit_graph({ label = paste(est_sig_std, "\n", confint_std) }) %>%
  edit_graph({ label = paste(name ) }, element = "nodes") %>%
  edit_graph({label_size = 2}) %>%
  plot()
  
ggsave(filename = plot_name, width = 8, height = 4)
}
```

```{r}
lay = get_layout("","","","","wellbeing","","","", "SWL", "Pos","Neg", "P", "E",  "R", "M","A", rows = 2)
semGraph(fit1b,"Model1.jpeg")
```


```{r echo=FALSE}
lay <- get_layout("","","SWB", "","","PERMA","","","SWL", "Pos","Neg", "P", "E",  "R", "M","A", rows = 2)
semGraph(fit2, "Model2.jpeg")
```
```{r}
lay = get_layout("","","SWB", "","","PERMA","","","SWL", "Pos","Neg", "P", "E",  "R", "M","A", rows = 2)
semGraph(fit3, "Model3.jpeg")
```
```{r}
lay = get_layout("","","SWB", "","","ERMA","","","SWL", "Neg",  "E",  "R", "M","A", rows = 2)
semGraph(fit4, "Model4.jpeg")
```



## Network Perspective

We then created four network models. Model 1 used just the PERMA questions, model 2 was PERMA plus negative emotions (N) and health (H). Model 3 we only modeled subjective well-being with model 4 combing subjective well-being. For each model we divided the data into a exploratory set to find the network structure and a confirmatory set to confirm the fit of the network to the data. All four models have adequete fit (see Table 3).  

```{r include=FALSE}
ExploratoryNetwork <- function(Explore){
  n_1 <- dim(Explore)[1]
  cor1 <- cor(Explore)
  
 
  ny <- length(colnames(Explore))
  
  saturatedModel <- ggm( covs = ( n_1 - 1 )/n_1*cor1,
                          omega = "Full",
                          nobs = n_1 )

  prunedModel <- saturatedModel %>% prune( alpha = 0.01, recursive = TRUE )
  finalModel  <- prunedModel %>% stepup
  adjacency <- 1*( getmatrix(finalModel, "omega" ) !=0 )
  return(adjacency)
}
```

```{r include=FALSE}
## Confirmatory modeling
confirmatoryNetwork <- function(confirm, adjacency,Model){
  n_2 <- dim(confirm)[1]
  cor2 <- cor(confirm)

  nwModel <- ggm( covs = ( n_2 - 1 )/n_2*cor2,
                omega = adjacency,
                nobs = n_2) 
 
  nwModel <- nwModel %>% runmodel
  
  matrix <- getmatrix( nwModel, "omega" )
  
  ## Compare
  result_nw <- fit(nwModel)
  
  
  results <- result_nw %>%  
    mutate(model = Model) %>% 
    filter(Measure %in% c('chisq',"df",'pvalue', 'tli','cfi','rmsea','aic.ll', 'bic','ebic1'))
  
  return(list(results = results,matrix = matrix))
 
}

```

```{r include=FALSE}
set.seed(2)
explore <- sample(1:nrow(dat), nrow(dat)*.5, replace = F)
```

```{r include=FALSE}
## PERMA NETWORK
PERMA_Explore <- dat[explore,]%>% 
  select(P1,P2,P3,E1,E2,E3,R1,R2,R3,M1,M2,M3,A1,A2,A3) 

PERMA_confirm <- dat[-explore,] %>% 
  select(P1,P2,P3,E1,E2,E3,R1,R2,R3,M1,M2,M3,A1,A2,A3)

yvars = colnames(PERMA_Explore)

lvars <- c( 
  "P", # Positive emttions
  "E", # Engagement
  "R", # Relationships
  "M",  # Meaning
  "A"  #Accomplishment
)

ne <- length( lvars )


lambda <- matrix( c (
  #P  E  R  M  A   
  1, 0, 0, 0, 0, #P1
  1, 0, 0, 0, 0,# P2
  1, 0, 0, 0, 0,# P3
  0, 1, 0, 0, 0,# MR
  0, 1, 0, 0, 0,# VC
  0, 1, 0, 0, 0,# AR 
  0, 0, 1, 0, 0,# SS
  0, 0, 1, 0, 0,# VP
  0, 0, 1, 0, 0,# IN
  0, 0, 0, 1, 0,# CD
  0, 0, 0, 1, 0,# LN
  0, 0, 0, 1, 0,# FW  
  0, 0, 0, 0, 1,# CO
  0, 0, 0, 0, 1,# CA
  0, 0, 0, 0,  1# PC
), 
ncol = ne, 
byrow = TRUE,
dimnames = list( yvars, lvars ) 
)
```

```{r include=FALSE}
## Exploratory 
adjacency <- ExploratoryNetwork(PERMA_Explore)
```

```{r}
colnames(adjacency) <- yvars
rownames(adjacency) <- yvars
write.csv(adjacency,"PERMA_adjacency.csv")
```

```{r include = FALSE}
results_PERMA <- confirmatoryNetwork(PERMA_confirm,adjacency, "PERMA")
```

```{r echo=FALSE}
jpeg("permaGraph.jpeg")

qgraph::qgraph( results_PERMA$matrix, 
        labels = yvars[1:15],
         groups = list( `Positive Emotions`   = which( lambda[ , 1 ] == 1 ),
                       Engagement        = which( lambda[ , 2 ] == 1 ),
                       Relationships = which( lambda[ , 3 ] == 1 ),
                       Meaning         = which( lambda[ , 4 ] == 1 ), 
                        Accomplishment   = which( lambda[ , 5 ] == 1 )),
        layout = "spring" )
dev.off()
```



```{r include=FALSE}
PERMANH_Explore <- dat[explore,]%>% 
  select(P1,P2,P3,E1,E2,E3,R1,R2,R3,M1,M2,M3,A1,A2,A3,N1, N2, N3, H1, H2, H3) 

PERMANH_confirm <- dat[-explore,] %>% 
  select(P1,P2,P3,E1,E2,E3,R1,R2,R3,M1,M2,M3,A1,A2,A3,N1, N2, N3, H1, H2, H3)

yvars = colnames(PERMANH_Explore)
ny <- length(colnames(PERMANH_Explore))

lvars <- c( 
  "P", # Positive emttions
  "E", # Engagement
  "R", # Relationships
  "M",  # Meaning
  "A",  #Accomplishment
  "N",
  "H"
)

ne <- length( lvars )


lambda <- matrix( c (
  #P  E  R  M  A N H  
  1, 0, 0, 0, 0, 0, 0, #P1
  1, 0, 0, 0, 0, 0, 0,# P2
  1, 0, 0, 0, 0, 0, 0,# P3
  0, 1, 0, 0, 0, 0, 0,# MR
  0, 1, 0, 0, 0, 0, 0,# VC
  0, 1, 0, 0, 0, 0, 0,# AR 
  0, 0, 1, 0, 0, 0, 0,# SS
  0, 0, 1, 0, 0, 0, 0,# VP
  0, 0, 1, 0, 0, 0, 0,# IN
  0, 0, 0, 1, 0, 0, 0,# CD
  0, 0, 0, 1, 0, 0, 0,# LN
  0, 0, 0, 1, 0, 0, 0,# FW  
  0, 0, 0, 0, 1, 0, 0,# CO
  0, 0, 0, 0, 1, 0, 0,# CA
  0, 0, 0, 0, 1, 0, 0,# PC
  0, 0, 0, 0, 0, 1, 0,
  0, 0, 0, 0, 0, 1, 0,
  0, 0, 0, 0, 0, 1, 0,
  0, 0, 0, 0, 0, 0, 1,
  0, 0, 0, 0, 0, 0, 1,
  0, 0, 0, 0, 0, 0, 1
  ), 
ncol = ne, 
byrow = TRUE,
dimnames = list( yvars, lvars ) 
)
```

```{r include=FALSE}
## Exploratory 
adjacency <- ExploratoryNetwork(PERMANH_Explore)
```


```{r}
colnames(adjacency) <- yvars
rownames(adjacency) <- yvars
write.csv(adjacency,"PERMA+NH_adjacency.csv")
```


```{r include=FALSE}
## Confirmatory modeling
results_PERMANH <- confirmatoryNetwork(PERMANH_confirm,adjacency, "PERMA+NH")
```

```{r echo = FALSE}
jpeg("permanhGraph.jpeg")
qgraph::qgraph(results_PERMANH$matrix, 
        labels = yvars[1:21],
         groups = list( `Positive Emotions`   = which( lambda[ , 1 ] == 1 ),
                       Engagement        = which( lambda[ , 2 ] == 1 ),
                       Relationships = which( lambda[ , 3 ] == 1 ),
                       Meaning         = which( lambda[ , 4 ] == 1 ), 
                        Accomplishment   = which( lambda[ , 5 ] == 1 ),
                      `Negative Emotions`       = which( lambda[ , 6 ] == 1 ),
                       Health = which( lambda[ , 7 ] == 1 )),
        layout = "spring" )
dev.off()
```


```{r include=FALSE}
SWB_Explore <- dat[explore,]%>% 
  select(SWL_1:PANAS_13) 

SWB_confirm <- dat[-explore,] %>% 
  select(SWL_1:PANAS_13)

yvars = colnames(SWB_Explore)
ny <- length(colnames(SWB_Explore))

lvars <- c( 
  "SWL", 
  "POS",
  "Neg"
)


ne <- length( lvars )


lambda <- matrix( c (
#SWL POS Neg   
  1, 0, 0, #SWL1
  1, 0, 0,# 2
  1, 0, 0,# 3
  1, 0, 0,# 4
  1, 0, 0,# 5
  0, 1, 0,# 1 
  0, 0, 1,# 2
  0, 1, 0,# 3
  0, 0, 1,# 4
  0, 1, 0,# 5
  0, 0, 1,# 6
  0, 1, 0,# 7  
  0, 0, 1,# 8
  0, 1, 0,# 9
  0, 0, 1,# 10
  0, 1, 0, # 11
  0, 0, 1, # 12
  0, 1, 0 # 13
  ), 
ncol = ne, 
byrow = TRUE,
dimnames = list(yvars, lvars ) 
)
```

```{r include = False}
## Exploratory
adjacency  <- ExploratoryNetwork(SWB_Explore)
```

```{r}
colnames(adjacency) <- yvars
rownames(adjacency) <- yvars
write.csv(adjacency,"SWB_adjacency.csv")
```

```{r include = False}
## Exploratory
results_SWB  <- confirmatoryNetwork(SWB_confirm,adjacency, "SWB")
```
```{r echo = FALSE}
jpeg("swbGraph.jpeg")
qgraph::qgraph( results_SWB$matrix, 
        labels = yvars,
         groups = list( `Satisfaction with Life`  = which( lambda[ , 1] == 1 ),
                       `Positive Affect`        = which( lambda[ ,2] == 1 ),
                      `Negative Affect`        = which( lambda[ ,3 ] == 1 )),
        layout = "spring" )
dev.off()
```

```{r include=FALSE}

PERMANHSWB_Explore <- dat[explore,] %>% 
  select(P1:PANAS_13)

PERMANHSWB_confirm <- dat[-explore,]%>% 
  select(P1:PANAS_13)

yvars = colnames(PERMANHSWB_Explore )
ny <- length(colnames(PERMANHSWB_Explore))

lvars <- c( 
  "P", # Positive emttions
  "E", # Engagement
  "R", # Relationships
  "M",  # Meaning
  "A",  #Accomplishment
  "N",
  "H",
  "SWL", 
  "POS",
  "Neg"
)


ne <- length( lvars )



lambda <- matrix( c (
  #P  E  R  M  A N  H  SWL Pos Neg 
  1, 0, 0, 0, 0, 0, 0, 0,0, 0, #P1
  1, 0, 0, 0, 0, 0, 0, 0,0, 0,# P2
  1, 0, 0, 0, 0, 0, 0, 0,0, 0,# P3
  0, 1, 0, 0, 0, 0, 0, 0,0, 0,# MR
  0, 1, 0, 0, 0, 0, 0, 0,0, 0,# VC
  0, 1, 0, 0, 0, 0, 0, 0,0, 0,# AR 
  0, 0, 1, 0, 0, 0, 0, 0,0, 0,# SS
  0, 0, 1, 0, 0, 0, 0, 0,0, 0,# VP
  0, 0, 1, 0, 0, 0, 0, 0,0, 0,# IN
  0, 0, 0, 1, 0, 0, 0, 0,0, 0,# CD
  0, 0, 0, 1, 0, 0, 0, 0,0, 0,# LN
  0, 0, 0, 1, 0, 0, 0, 0,0, 0,# FW  
  0, 0, 0, 0, 1, 0, 0, 0,0, 0,# CO
  0, 0, 0, 0, 1, 0, 0, 0,0, 0,# CA
  0, 0, 0, 0, 1, 0, 0, 0,0, 0,
  0, 0, 0, 0, 0, 1, 0, 0, 0, 0,
  0, 0, 0, 0, 0, 1, 0, 0, 0, 0,
  0, 0, 0, 0, 0, 1, 0, 0, 0, 0,
  0, 0, 0, 0, 0, 0, 1, 0, 0, 0,
  0, 0, 0, 0, 0, 0, 1, 0, 0, 0,
  0, 0, 0, 0, 0, 0, 1, 0, 0, 0,
  0, 0 ,0, 0, 0, 0, 0, 1, 0, 0, #SWL1
  0, 0 ,0, 0, 0, 0, 0, 1, 0, 0,# 2
  0, 0 ,0, 0, 0, 0, 0, 1, 0, 0,# 3
  0, 0 ,0, 0, 0, 0, 0, 1, 0, 0,# 4
  0, 0 ,0, 0, 0, 0, 0, 1, 0, 0,# 5
  0, 0 ,0, 0, 0,0,0, 0,  1, 0,# 1 
  0, 0 ,0, 0, 0,0, 0, 0, 0, 1,# 2
  0, 0 ,0, 0, 0,0, 0, 0, 1, 0,# 3
  0, 0 ,0, 0, 0,0,0, 0, 0, 1,# 4
  0, 0 ,0, 0, 0,0,0, 0, 1, 0,# 5
  0, 0 ,0, 0, 0,0, 0, 0,1, 0,# 6
  0, 0 ,0, 0, 0,0,0, 0, 0, 1,# 7  
  0, 0 ,0, 0, 0,0,0, 0, 1, 0,# 8
  0, 0 ,0, 0, 0,0,0, 0, 0, 1,# 9
  0, 0 ,0, 0, 0,0,0, 0, 0, 1,# 10
  0, 0 ,0, 0, 0,0,0, 0, 1, 0, # 11
  0, 0 ,0, 0, 0,0,0, 0, 0, 1, # 12
  0, 0 ,0, 0, 0,0, 0, 0,1, 0# PC
), 
ncol = ne, 
byrow = TRUE,
dimnames = list( yvars, lvars ) 
)
```

```{r include = FALSE}
## Exploratory
adjacency <- ExploratoryNetwork(PERMANHSWB_Explore)
```

```{r}
colnames(adjacency) <- yvars
rownames(adjacency) <- yvars
write.csv(adjacency,"PERMA+NH+SWB_adjacency.csv")
```

```{r include = FALSE}
### Network confirmatory
results_nwSWB_PERMA <- confirmatoryNetwork(PERMANHSWB_confirm, adjacency, "PERMA+NH+SWB")
```

```{r echo=FALSE}
jpeg("permanhSwbGraph.jpeg")
qgraph::qgraph( results_nwSWB_PERM$matrix, 
        labels = yvars,
        groups = list( `Positive Emotions`   = which( lambda[ , 1 ] == 1 ),
                       Engagement        = which( lambda[ , 2 ] == 1 ),
                       Relationships = which( lambda[ , 3 ] == 1 ),
                       Meaning         = which( lambda[ , 4 ] == 1 ), 
                        Accomplishment   = which( lambda[ , 5 ] == 1 ),
                      `Negative Emotions`       = which( lambda[ , 6 ] == 1 ),
                       Health = which( lambda[ , 7 ] == 1 ),
                       `Satisfaction with Life`         = which( lambda[ , 8 ] == 1 ),
                       `Positive Affect`        = which( lambda[ ,9 ] == 1 ),
                      `Negative Affect`        = which( lambda[ ,10 ] == 1 )),
        layout = "spring" )
dev.off()
```


## Compare models fit indeces

```{r include=FALSE}
## Compare
results_SWB_PERMA <-  results_nwSWB_PERMA$results %>%  
  mutate(model = "SWB + PERMANH") %>% 
  filter(Measure %in% c('chisq',"df",'pvalue', 'tli','cfi','rmsea','aic.ll', 'bic','ebic1'))

results_SWB <- result_SWB %>%  
  mutate(model = "SWB") %>% 
  filter(Measure %in% c('chisq',"df",'pvalue', 'tli','cfi','rmsea','aic.ll', 'bic','ebic1'))

results_network <-  results_PERMA$results %>% 
  rbind(results_PERMANH$results) %>% 
  #rbind(results_SWB) %>% 
  rbind(results_nwSWB_PERMA$results) %>%
  pivot_wider(names_from = "Measure", values_from = "Value")

names(results_network) <- c("Model","df", "$\\chi^2$", "p", "TLI", "CFI", "RMSEA","AIC", "BIC", "EBIC")
```


```{r fit tableNetwork, echo=FALSE}
results_network %>% 
     knitr::kable("latex",booktabs=TRUE) %>% 
     kableExtra::kable_styling()
```

## Network Loadings


```{r include=FALSE}
 loadings <- dat %>% 
  select(P1:PANAS_13) %>%
  EGAnet::EGA() %>% 
  EGAnet::net.loads()

load_df <- as.data.frame(loadings$std)
```

```{r net loadings table, echo=FALSE}
load_df %>% 
  arrange(match(rownames(load_df), c("P1","P2","P3","E1","E2","E3","R1","R2","R3","M1","M2","M3","A1","A2","A3", "N1","N2","N3", "H1","H2", "H3",'SWL_1','SWL_2','SWL_3','SWL_4','SWL_5','PANAS_1','PANAS_2','PANAS_3','PANAS_4','PANAS_5','PANAS_6','PANAS_7','PANAS_8','PANAS_9','PANAS_10','PANAS_11','PANAS_12','PANAS_13')))%>% 
     knitr::kable("latex",booktabs=TRUE) %>% 
     kableExtra::kable_styling()
```